Hypertension and microbiome

### 2019-04-29 articletwo.Rmd
Lactobacillus species level calulations removed

```{r core taxa}
pseq.genus.core <- core(pseq.genus, detection = 0.001, prevalence = 0.01)
pseq.species.lactobacillus <- subset_taxa(pseq.species, Genus=="Lactobacillus")
pseq.species.lactobacillus.core <- core(pseq.species.lactobacillus, detection = 0.001, prevalence = 0.01)
```

At genus level core has number of taxa `r ntaxa(pseq.genus.core)` (`r
ntaxa(pseq.genus)`). For lactobacilli core has number of taxa `r
ntaxa(pseq.species.lactobacillus.core)` (`r ntaxa(pseq.species.lactobacillus)`).

```{r maalin manual, eval = FALSE}
test.abud <- microbiome::abundances(microbiome::transform(pseq.genus.core, "compositional")) %>%
    t %>%
    as.data.frame
df <- test.abud %>% mutate_all(funs(asin(sqrt(.))))
```

```{r maaslin runs, results = 'hide'} 
maaslin <- list()

maaslin$genus <- maaslinwrapper(pseq = pseq.genus.core,
                looped = c("MAP", "SYSTM", "DIASM", "PULSEPRESSURE", "HYPERTENSION"),
                forced = c("BL_AGE", "SEX", "BMI", "CURR_SMOKE", "Q57X", "DIAB", "BL_USE_RX_C03",
                           "BL_USE_RX_C07", "BL_USE_RX_C08", "BL_USE_RX_C09"),
                taxa = "Halapricum.Archaea-")

lactotaxa <-c("Lactobacillus_delbrueckii.Bacteria", "Lactobacillus_ruminis.Bacteria", "Lactobacillus_acidophilus.Bacteria",
                    "Lactobacillus_fermentum.Bacteria", "Lactobacillus_paracasei.Bacteria", "Lactobacillus_salivarius.Bacteria")

maaslin$lacto.min <- maaslinwrapper(pseq = pseq.species.lactobacillus.core,
                looped = c("MAP", "SYSTM", "DIASM", "PULSEPRESSURE", "HYPERTENSION"),
                forced = c("BL_AGE", "SEX"),
                taxa =  paste0(lactotaxa,  collapse = ","))

maaslin$lacto.max  <- maaslinwrapper(pseq = pseq.species.lactobacillus.core,
                looped = c("MAP", "SYSTM", "DIASM", "PULSEPRESSURE", "HYPERTENSION"),
                forced =c("BL_AGE", "SEX", "BMI", "CURR_SMOKE", "Q57X", "DIAB", "BL_USE_RX_C03",
                          "BL_USE_RX_C07", "BL_USE_RX_C08", "BL_USE_RX_C09"),
                taxa = paste0(lactotaxa, collapse = ","))

```

>>>>

```{r core taxa}
pseq.genus.core <- core(pseq.genus, detection = 0.001, prevalence = 0.01)
```

```{r maaslin runs, results = 'hide'} 
maaslin <- list()
maaslin$genus <- maaslinwrapper(pseq = pseq.genus.core,
                looped = c("MAP", "SYSTM", "DIASM", "PULSEPRESSURE", "HYPERTENSION"),
                forced = c("BL_AGE", "SEX", "BMI", "CURR_SMOKE", "Q57X", "DIAB", "BL_USE_RX_C03",
                           "BL_USE_RX_C07", "BL_USE_RX_C08", "BL_USE_RX_C09"),
                taxa = "Halapricum.Archaea-")
```
